---
title: "Test 2"
author: "Anna Bartel"
output:
  pdf_document:
    keep_tex: true
    citation_package: natbib
---

```{r global-options, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.table.format = "latex") 
```

# Results

## Car Fuel Economy

This dataset contains a subset of the fuel economy data that the EPA makes available. It contains only models which has a new release every year between 1999 and 2008 -- this was used as a proxy for the popularity of the car. 

In order to ananlyze this data, we first created a new variable that averaged city miles per gallon and highway miles per gallon into one composite average miles per gallon. We were interested in assessing whether automatic or manual vehicles used more average miles per gallon. Please review the table below: 

```{r cars}

library(ggplot2)
library(tidyverse)

if (!require(ggplot2)) install.packages('ggplot2')
d <- mpg

d <- mutate(d,
             `avg_mpg` = (cty + hwy) / 2)

d <- d %>% 
  mutate(trans_ = str_sub(string = trans, 
                          start = 1, 
                          end = 1)) %>%  # extract first letter from trans
  mutate(`transmission_type` = case_when(trans_ == "a" ~ "automatic",
                                         trans_ == "m" ~ "manual",
                                         TRUE ~ "NA")) %>% 
  select(-trans_)

summarise(group_by(d, transmission_type),
          `mean avg_mpg` = mean(avg_mpg),
          'sd avg_mpg' = sd(avg_mpg))
```

We conducted a linear model where we regressed the average miles per gallon on transmission type. Results indicate that people who drive manual cars, on average, use more miles per gallon (M = 22.23, SD = 5.16) than people who drive automatic vehicles (M = 19.13, SD = 4.68), t(232) = 4.60, p < .001. 

```{r model}
mod <- lm(avg_mpg ~ transmission_type, data=d)
summary(mod, t = F)
```

Please refer to the Figure below. 

```{r plot, echo=FALSE}
theme_set(theme_classic())
g <- ggplot(d, aes(transmission_type, avg_mpg))
g + geom_boxplot(width = .2, fill="plum") + 
    labs(title="Box plot", 
         subtitle="Average Miles per Gallon grouped by Tranmission Type",
         caption="Source: mpg",
         x="Transmission Type",
         y="Average Miles per Gallon")
```
